MSA Asthma Place of Service Timeseries

### 2018-07-09 r_scripts/analysis/msa_asthma_timeseries.Rmd
updated contrast estimates to figure out diff in diff.

```{r saba_df}
saba = read_csv("../../data/health/2013-oregon_casecross_saba.csv") %>% 
  rename(identifier = personkey, ZIP = ZIPCODE) %>% 
  mutate(service_place = "SABA Fill",
         dx1 = ndc) %>% 
  # keeping only vars in the other casecrossover dataframes
  dplyr::select(vars_keep, ndc) %>% 
  # turn in to list
  list()

@@

Load Jingyang's mothly count to extract populations for MSA.
```{r msa_pop}
# read saba and asthma ed count# read  
population <- read_csv("./data/health/saba_month_counts.csv") %>% 
  select(msa_name, POPESTIMATE2013) %>% 
  rename(metroarea = msa_name,
         pop = POPESTIMATE2013) %>% 
  unique()
```

@@

```{r msa_pm}
# read saba
path = paste0('../../data/health/or_respiratory_may_to_sep_time_strat_casecross_er.csv')

# read respiratory casecross and find unique zipcodes by MSA values
zip_msa = read_csv(path, col_types = cols(.default = "c")) %>% 
    select(ZIPCODE, MSA) %>% 
    unique()

@@

    contr_msa_jul_to_sep <- rbind(
      #'Bend: Aug to Jul' = c(0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
      #'Bend: Aug to Sept' = c(0,0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
      #'Cor: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0,0,0),
      #'Cor: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0),
      #'Eug: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0,0),
      #'Eug: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0),
      'Med: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0),
      'Med: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0),
      'M v B: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,-1,0,0,1,0,0,0,0,0,0,0),
      'M v C: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,-1,0,1,0,0,0,0,0,0,0),
      'M v E: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,-1,1,0,0,0,0,0,0,0),
      'M v P: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,-1,1,0,0,0,0,0,0),
      'M v S: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,-1,0,1,0,0,0,0,0)
      #'Port: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0),
      #'Sal: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0),
      #'Sal: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1)
      )

    # multicomp comparison of contrasts
    jul_sep_contrast <- multcomp::glht(mod, contr_msa_jul_to_sep)
    # summary of adjusted
    compare_df <- data.frame(broom::tidy(
      summary(jul_sep_contrast, test = multcomp::adjusted('none')))) %>% 
      mutate(service_place = serv_pl) %>% 
      select(service_place, lhs:p.value)
  })
compare_df
```

Test change by MSA.

```{r}
print(saba_count)
```

>>>>

```{r saba_df}
saba <- read_csv("./data/health/2013-oregon_casecross_saba.csv") %>% 
  rename(identifier = personkey, ZIP = ZIPCODE) %>% 
  mutate(service_place = "SABA Fill",
         dx1 = ndc) %>% 
  # keeping only vars in the other casecrossover dataframes
  dplyr::select(vars_keep, ndc) %>% 
  # turn in to list
  list()

@@

Load Jingyang's mothly count to extract populations for MSA.
```{r msa_pop}
# read saba and asthma ed count# read  
population <- read_csv("./data/health/saba_month_counts.csv") %>% 
  dplyr::select(msa_name, POPESTIMATE2013) %>% 
  rename(metroarea = msa_name,
         pop = POPESTIMATE2013) %>% 
  unique()

```

@@

```{r msa_pm}
# read saba
path = paste0('./data/health/or_respiratory_may_to_sep_time_strat_casecross_er.csv')

# read respiratory casecross and find unique zipcodes by MSA values
zip_msa = read_csv(path, col_types = cols(.default = "c")) %>% 
    dplyr::select(ZIPCODE, MSA) %>% 
    unique()

@@

    contr_msa_jul_to_sep <- rbind(
      'Med: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0),
      'Med: Aug to Sept' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0),
      'M v B: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,1,0,-1,0,0,1,0,0,0,0,0,0,0),
      'M v C: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,-1,0,1,0,0,0,0,0,0,0),
      'M v E: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,-1,1,0,0,0,0,0,0,0),
      'M v P: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,1,0,0,0,-1,1,0,0,0,0,0,0),
      'M v S: Aug to Jul' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,1,0,0,-1,0,1,0,0,0,0,0)
      )

    # multicomp comparison of contrasts
    jul_sep_contrast <- multcomp::glht(mod, contr_msa_jul_to_sep)
    # summary of adjusted
    compare_df <- data.frame(broom::tidy(
      summary(jul_sep_contrast, test = multcomp::adjusted('none')))) %>% 
      mutate(service_place = serv_pl) %>% 
      dplyr::select(service_place, lhs:p.value)
  })
compare_df
```

Difference in difference test model.
```{r diff_in_diff}
saba_count <- monthly_msa_counts %>% 
  # filter to SABA fill
  filter(service_place == 'SABA Fill') %>% 
  # filter to portland and medford to test
  filter(metroarea %in% c('Portland', 'Medford'))

# diff in rate is 49.24 from july to aug for medford and -2.47 for portland

# running linear model to figure out rate
mod <- glm(n_events ~ 0 + metroarea*month_name, 
              family = poisson(link='identity'), data = saba_count)

summary(mod)
```

Contrast on model.

```{r diff_in_diff_contrast}
city_cont <- rbind(
      'Med: Aug to Jul' = c(0,0,0,-1,1,0,0,0,0,0),
      'Port: Aug to Jul' = c(0,0,0,0,0,0,0,-1,1,0)
      )

# multicomp comparison of contrasts
within_contrast <- multcomp::glht(mod, city_cont)

summary(within_contrast)

city_cont
diff_cont <- rbind(
  'diff' = (city_cont['Med: Aug to Jul',] - city_cont['Port: Aug to Jul', ])
  )

diff <- multcomp::glht(mod, diff_cont)
# expecting 261 difference
summary(diff)
```

261 diff.

City difference in difference from July to August in cities compared to Medford.

```{r diff_in_diff_final}
# function list
diff_df <- outcome_list %>% 
  map_dfr(., function(df){

    city_cont <- rbind(
      'Med: Jul to Aug' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0),
      'Bend: Jul to Aug' = c(0,0,0,0,0,0,0,-1,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0),
      'Cor: Jul to Aug' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0,0,0),
      'Eug: Jul to Aug' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0,0,0),
      'Port: Jul to Aug' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0,0),
      'Salem: Jul to Aug' = c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,-1,0,0,0,0,1,0,0,0,0,0)
      )

    diff_cont <- rbind(
      'Med to Port diff' = (city_cont['Med: Jul to Aug',] - city_cont['Port: Jul to Aug', ]),
      'Med to Bend diff' = (city_cont['Med: Jul to Aug',] - city_cont['Bend: Jul to Aug', ]),
      'Med to Cor diff' = (city_cont['Med: Jul to Aug',] - city_cont['Cor: Jul to Aug', ]),
      'Med to Eug diff' = (city_cont['Med: Jul to Aug',] - city_cont['Eug: Jul to Aug', ]),
      'Med to Sal diff' = (city_cont['Med: Jul to Aug',] - city_cont['Salem: Jul to Aug', ])
    )

    # multicomp comparison of contrasts
    diff_contrast <- multcomp::glht(mod, diff_cont)

    # summary of adjusted
    diff_df <- data.frame(broom::tidy(
      summary(diff_contrast, test = multcomp::adjusted('none')))) %>% 
      mutate(service_place = serv_pl) %>% 
      dplyr::select(service_place, lhs:p.value)
  })
easy_read_p <- diff_df %>% 
  mutate(p = round(p.value, 3))
easy_read_p
```

```{r}

```
